The Transition from Massive Metal Free Stars to Dwarf Galaxies

### 2011-02-02 ms.tex
Adding figures for filtering mass and metal filling fractions.  Almost finished with the results section except for the halo details subsection.

We initialize the simulation with \textsc{grafic}
\citep{Bertschinger01} at $z = 130$ and use the cosmological
parameters from the 7-year WMAP $\Lambda$CDM+SZ+LENS best fit
\citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b
= 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the
variables having their usual definitions.  We use a maximum refinement
level of $l = 12$, resulting in a maximal comoving resolution of 1 pc.
We stop the simulation at $z=7$ to avoid any large-scale modes with $r
\sim L_{\rm box}/2$ entering the non-linear growth regime.  At the
final redshift, this simulation has $1.4 \times 10^8$ computational
cells.

@@

Simulations have shown that the characteristic mass of Pop III stars
$M_{\rm char} \sim 100~\Ms$.  They form in molecular clouds that
coexist with the dark matter halo center with limited fragmentation
occurring during their collapse; however \citet{2009Sci...325..601T}
and \citet{Stacy10_Binary} have recently shown that Pop III binaries
may form in a fraction of such haloes.

@@

The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
their lifetime and $E_{\rm ph} = 21.6$ eV, appropriate for a [Z/H] =
$-1.3$ population.  We note that lower-metallicity stars generate up
to 60\% more ionizing photons and might be underestimating the
radiative feedback \citep{Schaerer03}.  Nonetheless this study
provides an excellent first insight in the transition to Pop II SF, as
the metal enrichment is the key ingredient here.  For SN feedback,
these stars generate $6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$
after living for 4 Myr, which is injected into spheres with a radius
of 10 pc, using the same technique as the Pop III SNe.  However if the
resolution of the grid is less than 10/3 pc, we distribute the energy
into a $3^3$ cube surrounding the star particle.  In addition to
numerical stability, energy distribution across several cells instead
of a single cell has been shown to match cosmic SFRs better in galaxy
simulations at lower redshifts \citep{Smith10}.

@@

We perform eight different simulations with the same initial
conditions.  The fiducial model considers (a) primordial cooling with
9 species of hydrogen, helium, and molecular hydrogen, (b) a Pop III
IMF characteristic mass $M_{\rm char}$ = 100 \Ms, and (c) Pop II and
Pop III star formation.  We vary this model with the following
changes:

\begin{enumerate}
\item Radiative cooling from metal species.  We calculate a cooling
  curve with CLOUDY \citep{CLOUDY} and use the method of
  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
  cooling curve.  It is tabulated based on density, temperature,
  electron fraction, and total metallicity.
\item A critical metallicity of [Z/H] = --5 and --6, accounting for
  the case where dust cooling can induce low-mass fragmentation in
  these lower metallicities \citep{Omukai05, Schneider06_Frag}.
\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
  the abundance patterns of EMP stars and reionization as constaints,
  the data are best fit with IMFs favoring stars with masses between
  20--130 \Ms~\citep{Umeda03, Tumlinson06}.
\item Lyman-Werner radiation background.  We use the semi-analytical
  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
  optical depth to Thompson scattering, to calculate the LW background
  intensity, plotted in Fig. \ref{fig:uvb}.  In this semi-analytical
  model, we use a Pop III stellar mass of 100 \Ms, star formation
  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
  LW radiation from point sources are added to the background.  The
  intensity decreases after $z \sim 14$ because Pop II star formation
  becomes dominant, which produce less LW specific luminosity than Pop
  III stars that have surface temperatures of $T = 10^5$ K.  For
  computational convenience, we fit the background evolution with the
  function
%
  \begin{equation}
    \label{eqn:uvb}
    \log J_{21}(z) = A + Bz - Cz^2 + Dz^3 - Ez^4,
  \end{equation}
%
  where $(A,B,C,D,E) = (-2.356, 0.4562, 0.02680, 5.882 \times 10^{-4},
  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
  units of $10^{-21}$ \emis.  This fits the
  model data within 1\% in $6 \le z \le 30$ and is consistent with
  $J_{21}$ values in \citet{Trenti09_SFR}.
\item Pop II star formation only.  This model is useful to study the
  importance of treating Pop III star formation as single stars and
  their pair-instability and Type II SNe.
\item Pop II star formation only and no molecular hydrogen cooling.
  This model provides a good comparison to larger scale simulations
  where it is not computationally feasible to consider \hh~cooling or
  resolve the necessary scales for Pop III star formation.
\end{enumerate}

@@

Here we present the gaseous and stellar evolution of the high-redshift
dwarf galaxies that form in our simulations.  To illustrate its global
properties, we show the density-weighted projections of gas density,
temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of IGM
over this redshift range, where the ionized fraction is 0.XX at $z=7$.
The metallicity projections show the growth of metal-enriched bubbles,
starting first with enrichment from Pop III stars.  Then as time
progresses, the haloes enriched within these bubbles above $Z_{\rm
  cr}$ transition to Pop II star formation, enriching their host halo
and surrounding IGM.  In Fig. \ref{fig:mass_fn}, we show the halo mass
function, agreeing well with the analytic halo mass function of
\citet{Warren06}.  We identify the haloes with a friends-of-friends
(FOF) algorithm \citep{Davis85}.  The excess of low-mass haloes below
$M_{\rm DM} = 2 \times 10^6 \Ms$ is most likely associated with the
biased region in the lower-right region in the projections.
Furthermore, the uncertainities in different analytic halo mass
functions \citep[see][for a comparison]{Reed07} and halo
identification are comparable than these differences.  Our fidicual
model contains 38 galaxies with a total of 3640 Pop II star clusters
and captures the formation of 333 Pop III stars.

We split our presentation into two sets of analyses.  In one, we focus
on the evolution of the individual halo and galaxy properties of the
10 most massive haloes at $z=7$ to better understand their formation
process and progenitors.  We list the global properties of these
haloes at $z = 7$ in Table \ref{tab:halos}.  Second, we analyze the
statistics of the star formation and metal enrichment in all 38
galaxies.  We first present results on the frequency of Pop III star
formation and the chemical enrichment from their PISNe.  We then focus
on the evolution in the global halo properties, followed by a
description of their Pop II star formation histories, metallicity
distribution functions, and star formation rates.  We then present
their metal enrichment and lastly comment on unique details of
individual haloes.

\subsection{Pop III star formation}

\subsubsection{Number of Pop III stars}

@@

\subsubsection{Metal enrichment from pair-instability SNe}

In Figure \ref{fig:zhalo3}, we show the average \zthree~in all haloes
as a function of halo mass at $z =$ 7, 8, 9, and 10, and it is
strongly dependent on halo mass.  The \zthree~error bars mark the 25\%
and 75\% percentiles of the distribution at $M = M_{\rm halo}$ because
the underlying distribution is not necessarily Gaussian at all halo
masses.  Above $3 \times 10^7 \Ms$, all haloes enriched to $\zthree
\ga -4$ with little time evolution, further illustrating the
metallicity floor.  Below this halo mass, the distribution is roughly
bimodal composed of pristine and metal-enriched halos.

\li Add figure and describe metal filling fraction evolution.

@@

\begin{figure}
  \vspace{200pt}
  \caption{\label{fig:filtering} Halo filtering mass.}
\end{figure}

@@

Because of the severity of gas loss from outflows created by Pop III
stars and Jeans-smoothing of the adjacent filaments, the halo is
dependent on mergers to replenish their gas supply
\citep[cf.][]{Yoshida07, Wise08_Gal, Greif10}.  For a halo to accrete
from a pre-heated IGM at a given time, it must exceed the `filtering
mass' \citep{Hui98, Gnedin00},
%
\begin{equation}
  \label{eqn:filtering}
  M_{\rm F}^{2/3} = \frac{3}{a} \int^a_0 da^\prime M_{\rm J}^{2/3}(a^\prime)
  \left[ 1 - \left(\frac{a^\prime}{a}\right)^{1/2} \right],
\end{equation}
where $M_{\rm J}$ is the time-dependent Jeans mass in the IGM.  We
plot $M_{\rm F}$ in the pre-heated IGM\footnote{We define the
  pre-heated IGM as regions with $x_e > 10^{-3}$ and $\rho/\bar{\rho}
  < 10$, where $x_e$ is the electron fraction and $\bar{\rho}$ is the
  mean cosmic density.} in Figure \ref{fig:filtering}.  Because the
haloes that merge into Halo 0 had $M > M_{\rm F}$, its gas fraction
recovers to nearly the cosmic fraction.  In contrast, all of the other
massive haloes build up their masses through mergers with halos $M \la
M_{\rm F}$ that cannot accrete from the pre-heated IGM.

@@

\subsection{Pop II star formation}

\begin{figure*}
  \epsscale{2.0}
  \plotone{sfh1.eps}
  \epsscale{1.0}
  \caption{\label{fig:SFH} The scatter plots show the Pop II star
    formation history as a function of metallicity for the 10 most
    massive halos.  Halo 8 is not shown because it contains no stars.
    Each circle represents a star particle, whose area is proportional
    to its mass.  The open circles in the upper right represent $M =
    10^3$, $10^4$, and $10^5$ \Ms.  The dashed lines in the Halo 0
    panel guide the eye to two stellar populations that were formed in
    two satellite halos, merging at $z=7.5$.  The upper histogram
    shows the star formation rate.  The right histogram depicts the
    Pop II metallicity distribution function.}
\end{figure*}

@@

\begin{figure}
  \plotone{mlratios.eps}
  \caption{\label{fig:ML} Mass to light ratios.}
\end{figure}

\subsubsection{Star formation histories}

The scatter plots of Fig. \ref{fig:SFH} show the Pop II star formation
history as a function of metallicity for the 10 most massive halos.

We now focus on the star formation rates (SFR) and metallicity
distribution functions (MDF) of these histories, collapsing the
stellar population in the metallicity and time axes, respectively.

Note that the most massive halo ($M_{\rm tot} = 10^9 \Ms$) is
undergoing a starburst at $z=7$ and has a relatively high $M/L = 6$.
The lower mass galaxies show a spread in M/L over two orders of
magnitude, similar to the Sloan Digital Sky Survey (SDSS) observations
of local dSph galaxies \citep[e.g.][]{Strigari08}.

\subsubsection{Metal enrichment}

\begin{figure}
  \plotone{z2.eps}
  \caption{\label{fig:zhalo2} Halo metallicities.}
\end{figure}

\begin{figure}
  \plotone{ztot.eps}
  \caption{\label{fig:ztot} Halo metallicities.}
\end{figure}

>>>>

We initialize the simulation with \textsc{grafic}
\citep{Bertschinger01} at $z = 130$ and use the cosmological
parameters from the 7-year WMAP $\Lambda$CDM+SZ+LENS best fit
\citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b
= 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the
variables having their usual definitions.  We use a maximum refinement
level of $l = 12$, resulting in a maximal comoving resolution of 1 pc.
We stop the simulation at $z=7$ to avoid any large-scale modes with $r
\sim L_{\rm box}/2$ entering the non-linear growth regime.  At the
final redshift, this simulation has $1.4 \times 10^8$ computational
cells and required 250,000 CPU hours, using 512 cores.

@@

Simulations have shown that the characteristic mass of Pop III stars
$M_{\rm char} \sim 100~\Ms$.  They form in molecular clouds that
coexist with the dark matter halo center with limited fragmentation
occurring during their collapse; however recent work have shown that
Pop III binaries and star clusters may form in a fraction of such
haloes \citep{2009Sci...325..601T, Stacy10_Binary, Greif11_P3Cluster}.

@@

The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
their lifetime and $E_{\rm ph} = 21.6$ eV, appropriate for a [Z/H] =
$-1.3$ population.  We note that lower-metallicity stars generate up
to 60\% more ionizing photons and might be underestimating the
radiative feedback \citep{Schaerer03}.  Nonetheless this study
provides an excellent first insight in the transition to Pop II SF, as
the metal enrichment is the key ingredient here.  For SN feedback,
these stars generate $6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$
after living for 4 Myr, which is injected into spheres with a radius
of 10 pc, using the same technique as the Pop III SNe.  However if the
resolution of the grid is less than 10/3 pc, we distribute the energy
into a $3^3$ cube surrounding the star particle.  In the same region,
star particles also return ejected material with mass
%
\begin{equation}
  \label{eqn:SNmass}
  \Delta m_{\rm ej} = \frac{0.25 \; \Delta t \; M_\star} 
         {t_0 - 4\;\mathrm{Myr}}
\end{equation}
back to the grid at every timestep on the finest AMR level.  Here
$t_0$ = 20 Myr is the lifetime of the star particle.  This ejected gas
has solar metallicity $Z = 0.02$, resulting in a total metal yield $y
= 0.005$.  In addition to numerical stability, energy distribution
across several cells instead of a single cell has been shown to match
cosmic SFRs better in galaxy simulations at lower redshifts
\citep{Smith10}.

@@

We perform nine different simulations with the same initial
conditions.  The fiducial model considers (a) primordial cooling with
9 species of hydrogen, helium, and molecular hydrogen, (b) a Pop III
IMF characteristic mass $M_{\rm char}$ = 100 \Ms, (c) Pop II and Pop
III star formation, and (d) a critical metallicity of [Z/H] = --4.  We
vary this model with the following changes:

\begin{enumerate}
\item Additional radiative cooling from metal species.  We calculate a
  cooling curve with CLOUDY \citep{CLOUDY} and use the method of
  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
  cooling curve.  It is tabulated based on density, temperature,
  electron fraction, and total metallicity.
\item A critical metallicity of [Z/H] = --5 and --6, accounting for
  the case where dust cooling can induce low-mass fragmentation in
  these lower metallicities \citep{Omukai05, Schneider06_Frag}.
\item Higher Pop II metal yield of $y = 0.025$ that is consistent with
  average values in the Milky Way \citep{Madau96}.
\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
  the abundance patterns of EMP stars and reionization as constaints,
  the data are best fit with IMFs favoring stars with masses between
  20--130 \Ms~\citep{Umeda03, Tumlinson06}.
\item Lyman-Werner radiation background.  We use the semi-analytical
  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
  optical depth to Thompson scattering, to calculate the LW background
  intensity, plotted in Fig. \ref{fig:uvb}.  In this semi-analytical
  model, we use a Pop III stellar mass of 100 \Ms, star formation
  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
  LW radiation from point sources are added to the background.  The
  intensity decreases after $z \sim 14$ because Pop II star formation
  becomes dominant, which produce less LW specific luminosity than Pop
  III stars that have surface temperatures of $T = 10^5$ K.  For
  computational convenience, we fit the background evolution with the
  function
%
  \begin{equation}
    \label{eqn:uvb}
    \log_{10} J_{21}(z) = A + Bz + Cz^2 + Dz^3 + Ez^4,
  \end{equation}
%
  where $(A,B,C,D,E) = (-2.356, 0.4562, -0.02680, 5.882 \times 10^{-4},
  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
  units of $10^{-21}$ \emis.  This fits the
  model data within 1\% in $6 \le z \le 30$ and is consistent with
  $J_{21}$ values in \citet{Trenti09_SFR}.
\item Pop II star formation only.  This model is useful to study the
  importance of treating Pop III star formation as single stars and
  their pair-instability and Type II SNe.
\item Pop II star formation only and no molecular hydrogen cooling.
  This model provides a good comparison to larger scale simulations
  where it is not computationally feasible to consider \hh~cooling or
  resolve the necessary scales for Pop III star formation.
\end{enumerate}

@@

Here we present the gaseous and stellar evolution of the high-redshift
dwarf galaxies that form in our simulations.  To illustrate its global
properties, we show the density-weighted projections of gas density,
temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of IGM
over this redshift range, where the mass- and volume-averaged ionized
fraction are 0.431 and 0.417 at $z=7$, respectively.  The metallicity
projections show the growth of metal-enriched bubbles, starting first
with enrichment from Pop III stars.  Then as time progresses, the
haloes enriched within these bubbles above $Z_{\rm cr}$ transition to
Pop II star formation, enriching their host halo and surrounding IGM.
In Fig. \ref{fig:mass_fn}, we show the halo mass function, agreeing
well with the analytic halo mass function of \citet{Warren06}.  We
identify the haloes with a friends-of-friends (FOF) algorithm
\citep{Davis85}.  The excess of low-mass haloes below $M_{\rm DM} = 2
\times 10^6 \Ms$ is most likely associated with the biased region in
the lower-right region in the projections.  Furthermore, the
uncertainities in different analytic halo mass functions
\citep[see][for a comparison]{Reed07} and halo identification are
comparable than these differences.  Our fidicual model contains 38
galaxies with a total of 3640 Pop II star clusters and captures the
formation of 333 Pop III stars.

We split our presentation into two sets of analyses.  In one, we focus
on the evolution of the individual halo and galaxy properties of the
10 most massive haloes at $z=7$ to better understand their formation
process and progenitors.  We list the global properties of these
haloes in Table \ref{tab:halos}.  Second, we analyze the statistics of
the star formation and metal enrichment in all 38 galaxies.  We first
present results on the frequency of Pop III star formation and the
chemical enrichment from their PISNe.  We then focus on the evolution
in the global halo properties, followed by a description of their Pop
II star formation histories, metallicity distribution functions, and
star formation rates.  We then present their metal enrichment and
lastly comment on unique details of individual haloes.

\subsection{Number of Population III stars}

@@

@@

\begin{figure}
  \plotone{mfilter.eps}
  \caption{\label{fig:filtering} The halo filtering mass (thick solid;
    eq. \ref{eqn:filtering}) that estimates the minimum halo mass that
    can host star formation when accreting from a pre-heated IGM.  The
    thick dashed lines shows the Jeans mass of the ionized regions of
    the IGM.  We compare the halo mass histories of Haloes 0 and 4
    (thin dotted and dot-dashed), illustrating that star formation can
    commence after accreting sufficient mass or be suppressed when the
    filtering mass grows faster than the halo mass.}
\end{figure}

@@

Because of the severity of gas loss from outflows created by Pop III
stars and Jeans-smoothing of the adjacent filaments, the halo is
dependent on mergers to replenish their gas supply
\citep[cf.][]{Yoshida07, Wise08_Gal, Greif10}.  For a halo to accrete
from a pre-heated IGM at a given time, it must exceed the `filtering
mass' \citep{Hui98, Gnedin00},
%
\begin{equation}
  \label{eqn:filtering}
  M_{\rm F}^{2/3} = \frac{3}{a} \int^a_0 da^\prime M_{\rm J}^{2/3}(a^\prime)
  \left[ 1 - \left(\frac{a^\prime}{a}\right)^{1/2} \right],
\end{equation}
where $M_{\rm J}$ is the time-dependent Jeans mass in the IGM.  We
plot $M_{\rm F}$ in the pre-heated IGM\footnote{We define the
  pre-heated IGM as regions with $x_e > 10^{-3}$ and $\rho/\bar{\rho}
  < 10$, where $x_e$ is the electron fraction and $\bar{\rho}$ is the
  mean cosmic density.} in Fig. \ref{fig:filtering}.  This shows that
Halo 0 can accrete the pre-heated IGM to form stars after $z=11$ when
$M > M_{\rm F}$.  Halo 4 accretes most of its gas at $z>12$, always
above the filtering mass.  Afterwards it undergoes a quiescent
accretion period, becoming comparable to $M_{\rm F}$ and losing the
ability to accrete pre-heated IGM.

The gas fraction in Halo 0 recovers to nearly the cosmic fraction
because the haloes that merge into Halo 0 at $z=7.5$ have $M > M_{\rm
  F}$, allowing these merging haloes to have cold gas reservoirs.  In
contrast, all of the other massive haloes build up their masses
through mergers with halos $M \la M_{\rm F}$ that cannot accrete from
the pre-heated IGM.

@@

\subsection{Star formation in dwarf galaxies}

\begin{figure*}
  \epsscale{2.0}
  \plotone{sfh1.eps}
  \epsscale{1.0}
  \caption{\label{fig:SFH} The scatter plots show the Pop II star
    formation history as a function of stellar age $t_\star$ with
    respect to metallicity for the 10 most massive halos.  Halo 8 is
    not shown because it contains no stars.  Each circle represents a
    star particle, whose area is proportional to its mass.  The open
    circles in the upper right represent $M = 10^3$, $10^4$, and
    $10^5$ \Ms.  The dashed lines in the Halo 0 panel guide the eye to
    two stellar populations that were formed in two satellite halos,
    merging at $z=7.5$.  The upper histogram shows the star formation
    rate with each bar representing 5 Myr.  The right histogram
    depicts the Pop II metallicity distribution function.}
\end{figure*}

Here we present the properties of the metal-enriched stellar
population.  The SFHs of the 10 most massive haloes are shown in
Fig. \ref{fig:SFH} in the plane of stellar age $t_\star$ and
metallicity as scatter plots with each point representing a star
particle and its size proportional to its mass.  Collapsing the data
along the time and metallicity axes gives the metallicity distribution
function (MDF) and star formation rate, respectively, also shown in
the Figure.

\subsubsection{Star formation histories}
\label{sec:SFH}

One general trend in the most haloes is the correlation
between metallicity and time, which is expected in the case of
continuous enrichment from intrinsic and nearby star formation.  One
interesting except are the formation of [Z/H] $\sim$ --1 stars very
early in the SFHs of Haloes 0 and 3.  This occurs when a PISN
blastwave interacts with a pristine minihalo, enriching it and then
triggering relatively metal-rich star formation.

Halo 0 experiences an intense halo merger history.  This halo begins a
major merger at $z \sim 10$, and the gaseous structures finally
interact at $z \sim 8.5$.  This interaction produces a starburst that
enriches the star-forming gas, seen as a jump from [Z/H] $\sim$ --2 to
--1.5 in the SFH.  Star formation continues to enrich the halo,
leading to stellar metallicities [Z/H] $\sim$ --1 at $z=7$.  In
addition to the $z \sim 10$ major merger, it encounters two haloes
both with an established stellar component at $z \sim 7.5$.  Because
each halo SFH is unique, they are distinguishable in the final SFH
stellar age -- metallicity ($t-Z$) plot.  These relic stellar
populations are distinct, which are traced with dashed lines in
Fig. \ref{fig:SFH}, from the main $t-Z$ track.

Halo 1 also contains a relic stellar population.  Its main progenitor
follows a $t-Z$ trajectory from ($t = 300 \mathrm{Myr}, 10^{-3}
\zsun$) to ($t = 200 \mathrm{Myr}, 10^{-2} \zsun$) and plateaus
afterwards.  All of the stars with a lower metallicity than this track
belonged to the lesser halo that merges at $z=7.4$.  The plateau in
stellar metallicity is also seen in Halo 4, where self-enrichment
steadily increases the metallicity from [Z/H] = --2.8 at $z = 15$ to
[Z/H] = --2.0 at $z = 9.5$.  Then mass loss from metal-rich outflows
is balanced by metal-poor inflows from the filaments, causing the
stellar metallicity to plateau and not enrich the halo gas
considerably further.  The remainder of the haloes do not possess
enough star particles to gain substantial insight on their SFHs unless
we reduce the data along a variable and study their SFRs and MDFs.

Star formation rates above $10^{-2}$ \hsfr~begins in Halo 0 after the
$z=9$ major merger, which also increases its virial temperature above
\tento{4}~K, i.e. an atomic cooling halo.  The initial starburst
inhibits star formation for 20--40 Myr, reduced by a factor of $\sim
5$.  After this period of self-regulation, the SFR increases back to
$\sim 10^{-2}$ \hsfr, slowly increasing to $3 \times 10^{-2}$ \hsfr~at
$z=7$ with a burst at $z=7.4$ that accompanies another major merger.

Haloes 1, 3, and 4 support star formation in bursts with SFRs $\sim
10^{-3}$ \hsfr.  The bursts in Haloes 1, 3, and 4 have typical
durations of 40, 5, and 10 Myr, respectively.  As in Halo 0 but more
severe, self-regulation plays an important role in the buildup of
their stellar populations.  Because the potential wells of these
haloes are not deep enough to contain the dense, star-forming gas,
star formation is quenched for tens of Myr.  The remaining haloes
experience even more sporadic star formation events with typical rates
below \tento{-4}~\hsfr.

Halo 0 has the most interesting MDF with a bimodal distribution with
the two distributions centered at [Z/H] = --1.2 and --2.4.  The more
metal-poor population were formed either formed in the most massive
halo progenitors before the starburst at $z \sim 8.5$ or in the two
galaxies that merged at $z \sim 7.5$.  Rapid star formation during the
burst caused the typical metallicities to increase almost 1 dex over
30--50 Myr.  The dip in the MDF is caused by this rapid enrichment
because of the small fraction of stars formed during this period.
This bimodality is seen in the inner regions of the Sextans dSph
galaxies with the different distributions centered at [Fe/H] = --2.8
and --2.0 \citep{Battaglia10}.

All other haloes have stellar populations that are within 1 dex of
each other.  Incomplete metal mixing or local enrichment from SN
bubbles cause this spread in [Z/H].  The plateaus in the $t-Z$ plane
are distinugishable by their overabundance of stars at their maximum
metallicity.  In Haloes 1 and 4, The total mass in stars with
metallicities lower than the plateau is equal to the mass in the
metallicity plateau.  Haloes with relic stellar populations from prior
mergers cannot be disentangled from the MDF of total metallicity
alone.  However studying the individual abundances of stars should
reveal details about the SFH and merger history of local dwarf
galaxies \citep{Frebel10}.

@@

\begin{figure}
  \plotone{mlratios.eps}
  \caption{\label{fig:ML} Mass to light ratios as a function of halo
    mass at $z$ = 7, 8, 9, and 10.  Note that the ratios are largest
    at all masses at the latest time.  The points in each set are
    offset in the $x$-axis to increase clarity.}
\end{figure}

Mass-to-light ratios are crucial in interpreting observations when
connecting the galaxy to its DM halo, and ultimately to models of
galaxy formation.  For this paper, we use a simple model to calculate
the total stellar luminosity of each galaxy.  In a later paper, we
will follow up with more sophisicated models to determine more
accurate observables.  Stars in each particle are treated an
instantaneous burst.  Using the empirical law of main sequence
lifetime $t_{\rm MS} \propto M^{-5/2}$, the maximum stellar mass in
such a system is dependent only on its age, $M_{\rm up} = (t_\star /
10\;\mathrm{Gyr})^{-2/5}$.  Then combining another scaling law $L
\propto M^{7/2}$ and the Salpeter IMF $\psi(M) \propto M^{-\alpha}$,
%
\begin{eqnarray}
  \label{eqn:lum}
  L/M_\odot &=& \int_{M_{\rm lo}}^{M_{\rm up}} \psi(M) L(M) dM \nonumber\\
      &\simeq& M_{\rm up}^{9/2-\alpha} (9/2 - \alpha)^{-1},
\end{eqnarray}
where we set $M_{\rm lo} \equiv 0$ because it is negligible in the
luminosity.  Then the galaxy luminosity is the sum of all star
particle luminosities, which we plot in Fig. \ref{fig:Lstar} with
respect to halo mass.

Recall that the most massive halo ($M_{\rm tot} = 10^9 \Ms$) is
undergoing a starburst at $z=7$, translating into a relatively high
$M/L = 6$.  The lower mass galaxies show a spread in M/L over two
orders of magnitude, similar to the Sloan Digital Sky Survey (SDSS)
observations of local dSph galaxies \citep[e.g.][]{Strigari08}.

Fig. \ref{fig:ML} illustrates the change in the M/L ratio at four
different epochs, $z$ = 7, 8, 9, and 10.  At $z=10$, the galaxies
reside in haloes with $10^7 \la M/\Ms \la 10^8$ and have $\log
(\mathrm{M/L}) \sim 2 \pm 0.5$.  At redshift 8 and 9, stellar feedback
reduce the cold gas reservoirs for star formation, thus increasing the
average M/L values with the largest change at the lowest halo masses.
At $z=7$, stellar feedback and a pre-heated IGM begin to have a
noticable effect on all galaxies except for the most massive galaxy in
a $10^9 \Ms$ halo.  In these low mass galaxies,
$\langle\mathrm{M/L}\rangle \sim 1000$, trending slightly downward
with halo mass.  Also the spread of M/L is larger than at earlier
times because of differing galaxy environments.  Galaxies with higher
M/L ratios lie in biased regions, and the lower M/L galaxies are
isolated and avoid negative radiative feedback from neighboring
galaxies.

\subsection{Metal enrichment from pair-instability SNe}

\begin{figure}
  \plotone{z3fill.eps}
  \caption{\label{fig:z3fill} Mass fraction (thick lines) and volume
    filling fraction (thin lines) of material enriched by Pop III SNe
    above \zthree~= (-6, -5, -4, -3).}
\end{figure}

In Fig. \ref{fig:zhalo3}, we show the average \zthree~in all haloes as
a function of halo mass at $z =$ 7, 8, 9, and 10, and it is strongly
dependent on halo mass.  The \zthree~error bars mark the 25\% and 75\%
percentiles of the distribution at $M = M_{\rm halo}$ because the
underlying distribution is not necessarily Gaussian at all halo
masses.  Above $3 \times 10^7 \Ms$, all haloes enriched to $\zthree
\ga -4$ with little time evolution, further illustrating the
metallicity floor.  Below this halo mass, the distribution is roughly
bimodal composed of pristine and metal-enriched halos.

Fig. \ref{fig:z3fill} depicts the volume filling fraction $f_{\rm
  v,III}$ and mass fraction $f_{\rm m,III}$ of gas enriched above
metallicities \zthree~= (--6, --5, --4, --3).  The first PISN occurs
at $z = 16.5$, initially enriching $10^{-4}$ ($10^{-3}$) of the
simulation volume (mass).  The enriched gas mass (volume) fraction
with $\zthree > -6$ rises steadily with time to reach 0.14 (0.038) at
$z=7$.  The gas fraction enriched above \zthree~= (--5, --4, --3) are
15\%, 30\%, and 50\% lower, respectively, and these differences vary
little with time after the initial enrichment.  The ratio of the mass-
and volume-weighted enriched fractions $f_{\rm m,III}/f_{\rm v,III}
\sim 4$, which indicates the average overdensity in an enriched
region.  It also demonstrates that metal enrichment is an `inside-out'
process with the overdense regions being enriched first with the voids
an filaments later, similar to reionization.

\subsection{Metal enrichment from Pop II core collapse SNe}

\begin{figure}
  \plotone{ztot.eps}
  \caption{\label{fig:ztot} The fraction of haloes above an average
    gas metallicity of [Z/H] = --5 (top), --4 (middle), and --3
    (bottom) as a function of halo mass at $z$ = 7, 8, 10, and 12.}
\end{figure}

\begin{figure}
  \plotone{z2fill.eps}
  \caption{\label{fig:z2fill} Mass fraction (thick lines) and volume
    filling fraction (thin lines) of material enriched by Pop II SNe
    above \ztwo~= (-6, -5, -4, -3).}
\end{figure}

\begin{figure}
  \plotone{z2.eps}
  \caption{\label{fig:zhalo2} Average halo metallicity from Pop II SNe
    as a function of total halo mass.  Inhomogenous metal enrichment
    causes the large spread in metallicity at low masses.  At $M_{\rm
      halo} > 3 \times 10^7 \Ms$, halos can host Pop II star formation
    that self-enrich the gas, resulting in $\langle[Z_2/H]\rangle \sim
    -3$ at $M_{\rm halo} = 10^8 \Ms$.  The y-axis error bars show the
    25\% and 75\% percentile values because the underlying
    distribution is not Gaussian.}
\end{figure}

After Pop III star formation has ended in a region, Pop II stars then
form and further enrich the galaxy and its neighborhood.
Fig. \ref{fig:Zevo} also shows the average gas, \ztwo, and stellar,
[Z$_\star$/H], metallicities from Pop II SNe.  All haloes experience
an initial enrichment from Pop II stars to $-4 \la \ztwo \la -3$.
They are either initially enriched by intrinsic star formation or
external blastwaves.  This can be determined by comparing the onset of
metal enrichment in the gas and stars.  If the gas metallicity becomes
non-zero before the stellar metallicity (i.e. the start of Pop II star
formation), the halo was enriched from an external source.  This
happens most notably in Haloes 2, 3, and 7 with disprenacies of
100--200 Myr between the time when stellar and gas metallicities
become non-zero.

Halo 0 remains at \ztwo~= --3 before the starburst $z \sim 8.5$ and
then is subsequently and quickly enriched to \ztwo~= --2.  The
continuous star formation steadily enriches the gas to an average
\ztwo~= --1.3 by $z=7$.  All of the other haloes do not possess a deep
enough potential well to support such a starburst, and their
metallicites remain nearly constant with the expection of the haloes
with $\ztwo < -3$ that can have flucutations on the order of 0.5 dex
because averages of these low mass fractions are sensitive to even
small changes.  The metallicities from Pop II stars are equal or
smaller than Pop III stars in these low mass halos.

In general, the stellar metallicities follow the same trends as the
gas metallicities with the exception of Haloes 0 and 3.  Some of the
first metal-enriched stars were triggered by PISN blastwaves and have
relatively high [Z/H] $\sim$ --1 that skew the average above the gas
metallicity.  Subsequent star formation in these haloes have [Z/H]
values comparable to the average gas metallicity.  Haloes 2, 5, 6, and
9 have stellar metallicities that are dominated by PISNe enrichment,
seen as [Z$_\star$/H] = \zthree~when star formation commences in
Fig. \ref{fig:Zevo}.  Later star formation do not enrich the gas
considerably further as the outflows are not bound to the halo.

Fig. \ref{fig:ztot} quantifies the fraction of haloes at a given mass
are enriched above a mean total metallicity [Z/H] = --3, --4, and --5
at redshifts 7, 8, 10, and 12.  The minihaloes with $M \sim 10^6$ are
primarily enriched by PISNe and are nearly equal to the metal volume
filling fraction, shown in Fig. \ref{fig:z3fill}, for all metallicity
cuts.  The fraction linearly increases to approximately 0.6 for [Z/H]
= --3 and 0.8 for the [Z/H] = --4 and --5 cuts at a halo mass of
\tento{7}\Ms because these larger haloes have a higher probability
that one of its progenitors hosted a PISN.  For the lower two
metallicity cuts, the fraction continues to increase until all of the
haloes are enriched above $3 \times 10^7 \Ms$ and $10^8 \Ms$ for [Z/H]
= --4 and --5, respectively.  These trends are redshift independent
for the data shown here because the halo mass (with respect to the
filtering mass) is driving factor in controlling star formation and
metal production.  For the metallicity cut of [Z/H] = --3, there is
considerable noise from redshift to redshift.  But at redshift 7, all
of the haloes above \tento{8}\Ms are enriched above this level except
for Halo 2 (there are only 2 halos in the $2 \times 10^8 \Ms$ bin),
because it hosts too little star formation for significant
self-enrichment to occur.
